Stack Safety as a Security Property

### 2020-07-07 main.tex
More example fixes

For example, consider the unsafe substitution:
\[
42 : ~ \sw ~ r_4 ~ \rsp 100
\]
Instead of reading the proper argument, {\tt h} reads directly from the
secret value of {\tt x} that belongs to {\tt main}. \Cref{fig:confex}
shows \(\mach_e\), the entry state of {\tt h}, with high confidentiality memory
in magenta and low confidentiality in teal. Below it, the variant state
\(\mach_e'\) agrees on low confidentiality memory, but all other addresses
hold -5, in orange. After the last step, the return states \(\mach_r\) and
\(\mach_r'\) should agree on every component that changed since \(\mach_e\) or
\(\mach_e'\). Addresses 108 and 109 have changed, shown in gray, and while 109
is consistent, 108 holds either 43 or -4, so the trace does not obey
trace confidentiality.
\rb{Color name macros}

\sna{I like instantiating the variant, tomorrow I will extend it to the
     lazy example as well.}

@@

    For out example, we return to the violation of trace integrity in
    \cref{fig:intex}, in which {\tt h} has written to {\tt z} and returned.
    Whether observable integrity holds depends on the continuing trace, shown
    in \cref{fig:intlex}. Above, we have the final state of \(\MPT\),
    \(\mach_r\), with high integrity components in red and low integrity in
    green. Next is the rolled-back state, \(\mach_r' =
    \mathit{roll}(\contour,\mach_e,\mach_r)\), in which high integrity
    components are restored to their values as of \(\mach_e\). Specifically,
    address 103 is restored to 0. When instruction 31 prints {\tt z} in the
    trace from \(\mach_r\), it prints 18, but in the trace from \(\mach_r'\)
    it prints 0. So observable trace integrity does not hold.
    \rb{Color name macros}

@@

      In our example, \cref{fig:conflex} shows how execution continues from
      \(\mach_r'\) and the restored \(\mach_r'' = \mathit{restore}(\contour,
      \mach_e,\mach_e',\mach_r,\mach_r')\). Addresses 108 and 109, in \tainted,
      are not restored; every address that was varied and not changed in one
      of the executions is. Since 108 contains a value that originates in the
      variation, values that depend on it might be anything; after returning
      from {\tt g}, {\tt main} prints 95 in the trace from \(\mach_r\) and
      some undetermined value in the trace from \(\mach_r''\). So observable
      trace confidentiality does not hold.
      \rb{Color name macro}

>>>>

For example, consider the unsafe substitution:
\[
42 : ~ \sw ~ r_4 ~ \rsp 100
\]
Instead of reading the proper argument, {\tt h} reads directly from the
secret value of {\tt x} that belongs to {\tt main}. \Cref{fig:confex}
shows \(\mach_e\), the entry state of {\tt h}, with high confidentiality memory
in \high and low confidentiality in \low. Below it, the variant state
\(\mach_e'\) agrees on low confidentiality memory, but all other addresses
hold -5, in orange. After the last step, the return states \(\mach_r\) and
\(\mach_r'\) should agree on every component that changed since \(\mach_e\) or
\(\mach_e'\). Addresses 108 and 109 have changed, shown in \tainted, and while 109
is consistent, 108 holds either 43 or -4, so the trace does not obey
trace confidentiality.
\rb{Color name macros}

@@

    For out example, we return to the violation of trace integrity in
    \cref{fig:intex}, in which {\tt h} has written to {\tt z} and returned.
    Whether observable integrity holds depends on the continuing trace, shown
    in \cref{fig:intlex}. Above, we have the final state of \(\MPT\),
    \(\mach_r\), and the rolled-back state, \(\mach_r' =
    \mathit{roll}(\contour,\mach_e,\mach_r)\), in which high integrity
    components are restored to their values as of \(\mach_e\). Specifically,
    address 103 is restored to 0. When instruction 31 prints {\tt z} in the
    trace from \(\mach_r\), it prints 18, but in the trace from \(\mach_r'\)
    it prints 0. So observable trace integrity does not hold.

@@

      In our example, \cref{fig:conflex} shows how execution continues from
      \(\mach_r'\) and the restored \(\mach_r'' = \mathit{restore}(\contour,
      \mach_e,\mach_e',\mach_r,\mach_r')\). Addresses 108 and 109, in \tainted,
      are not restored; every address that was varied and not changed in one
      of the executions is. So 108 contains 43 in the trace from \(\mach_r\),
      and after returning from {\tt g}, {\tt main} prints 85. But in the trace
      from \(\mach_r''\), 108 contains -4, and ultimately 38 is printed.
      So observable trace confidentiality does not hold. This example
      illustrates the weakness of observable confidentiality as a testing
      property; it takes until the very end of the program to determine whether
      a tainted value actually influences observable behavior.
